---
title: "MOT_model_t"
author: "Kaiwen Lai"
date: "25/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(stringdist)
```

```{r}
df<-read.csv("../MOT Extract - Oct 2019.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
df_empty.ind <- apply(df, 1, function(x){
  sum(!is.na(x) & x !='' & !is.null(x))
}) 
df1 <- df[df_empty.ind!=0,]

sub.df <- df1 %>% select(make, make_n, mvrregmake_n, model, model_n, mvrregmodel_n, sub_model, submodel_n,mvrregsubmodel_n, body_style, seats, seats_n, transmission_n) %>% mutate_all(list(~tolower(.)))

get.Longest <- function(x){
  final.choice <- x[1]
  for(i in 1:length(x)){
    if(nchar(x[i])>nchar(final.choice)){
      final.choice <- x[i]
    }
  }
  final.choice
}

getModel <- function(x){
   x[x=="null"] <- NA
   x[x==""] <- NA
   noempty_x <- na.omit(x) # remove NA first
   noempty_table <- sort(-table(noempty_x)) # table of count in descending order
   new_table <- names(noempty_table) # attribute names from 'new_table'
   
   if(is.null(new_table)) {
     fn_code = 1
     res = "NONE" 
     } else {
       res = new_table[1]
       fn_code = 2
       # 1st should be the  majority
       if(length(new_table)>1 && noempty_table[1] == noempty_table[2]){
         res = get.Longest(new_table)
         fn_code = 3} # get longest one if 1st = 2nd 
       
     }
   return(res) 
}

new.df <- sub.df %>% mutate(
  finalmake = apply(data.frame(make, make_n, mvrregmake_n),1,getModel),
  finalmodel = apply(data.frame(model, model_n, mvrregmodel_n),1,getModel),
  finalsubmodel = apply(data.frame(sub_model, submodel_n,  mvrregsubmodel_n),1,getModel)) 
```

```{r}
head(new.df)
```

```{r}
stringsim("ca", c("abc","abd","cba","nba"),method="osa")
stringsim("ca", c("abc","abd","cba","nba"),method="lv")
stringsim("ca", c("abc","abd","cba","nba"),method="dl")
stringsim("ca", c("abc","abd","cba","nba"),method="hamming")
stringsim("ca", c("abc","abd","cba","nba"),method="lcs")
stringsim("ca", c("abc","abd","cba","nba"),method="qgram")
stringsim("ca", c("abc","abd","cba","nba"),method="cosine")
stringsim("ca", c("abc","abd","cba","nba"),method="jaccard")
stringsim("ca", c("abc","abd","cba","nba"),method="jw")
stringsim("ca", c("abc","abd","cba","nba"),method="soundex")
```






```{r}
dt1<-read.csv("../VehicleYear-2020.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt2<-read.csv("../VehicleYear-2019.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt3<-read.csv("../VehicleYear-2018.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt4<-read.csv("../VehicleYear-2017.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt5<-read.csv("../VehicleYear-2016.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt6<-read.csv("../VehicleYear-2015.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt7<-read.csv("../VehicleYear-2014.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt8<-read.csv("../VehicleYear-2013.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt9<-read.csv("../VehicleYear-2012.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt10<-read.csv("../VehicleYear-2011.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)

big_dt<-rbind(dt1,dt2,dt3,dt4,dt5,dt6,dt7,dt8,dt9,dt10)
```

```{r}
colnames(big_dt) <- tolower(colnames(big_dt))

sub.dt <- big_dt %>% select(make, model, submodel) %>% mutate_all(list(~tolower(.)))

dt_empty.ind <- apply(data.frame(sub.dt$submodel), 1, 
  function(x){
    sum(!is.na(x) & x !='' & !is.null(x))
}
)
sub.dt1 <- sub.dt[dt_empty.ind!=0,]

head(sub.dt1)
```


```{r}
sub.dt2 <- unique(sub.dt1)

dim(sub.dt1)
dim(sub.dt2)
```

```{r}
t1<-new.df
t2<-sub.dt2
#make,model,
```

```{r}
fit_submodel <- function(x,y=sub.dt2){
  sub_m <- x[2]
  mak <- x[1]
  
  if(sub_m!="NONE"){
    
    y_sub <- y[y[,1]==mak,]
    
    b<-stringsim(sub_m,y_sub[,"submodel"],method='osa')
    max.fit <- which.max(b)
    if(length(max.fit)==0){
      final.tag <- 0
    }else{
      a_sub <- y_sub[max.fit,"submodel"]
      a_make<- y_sub[max.fit,"make"]
      a_model <- y_sub[max.fit,"model"]
      final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    }
  }else{
    final.tag <- 0
  }
  
  final.tag
  
}


t1<-t1 %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_num = apply(data.frame(finalmake,finalsubmodel),1,fit_submodel))

head(t1,25)
```


How about the NONE sub-model?

```{r}
t3 <- t1 %>% filter(fit_num!=0)

t4 <- t3 %>% mutate( 
  base_make = sub.dt2$make[fit_num],
  base_model = sub.dt2$model[fit_num],
  base_submodel = sub.dt2$submodel[fit_num])
head(t4,20)
```
1. clean the source(make it smaller, get rid of duplicated value(same make,model,submodel))
2. filter the same make for each match, and get the highest similarity value as a result.



```{r}
dim(t4[t4$finalmodel==t4$base_model,])
```


Next, we try to find the record with same model and highest similarity of sub model.

```{R}
tb<-new.df

fit_submodel2 <- function(x,y=sub.dt2){
  mak <- x[1]
  mod <- x[2]
  s_mod <- x[3]
  
  if(s_mod!="NONE"){
    
    y_sub <- y[y[,1]==mak & y[,2]==mod,]
    
    b<-stringsim(s_mod,y_sub[,"submodel"],method='osa')
    max.fit <- which.max(b)
    if(length(max.fit)==0){
      final.tag <- 0
    }else{
      a_sub <- y_sub[max.fit,"submodel"]
      a_make<- y_sub[max.fit,"make"]
      a_model <- y_sub[max.fit,"model"]
      final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    }
  }else{
    final.tag <- 0
  }
  
  final.tag
  
}

tb<-tb %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_num = apply(data.frame(finalmake,finalmodel,finalsubmodel),1,fit_submodel2))

head(tb,25)

t3b <- tb %>% filter(fit_num!=0)

t4b <- t3b %>% mutate( 
  base_make = sub.dt2$make[fit_num],
  base_model = sub.dt2$model[fit_num],
  base_submodel = sub.dt2$submodel[fit_num])
head(t4b,20)
```
```{r}
dim(tb[tb$fit_num!=0,])
```

```{r}
head(tb[tb$fit_num==0,],20)
```


With the highest sum of similarity of model and submodel

```{R}
tc<-new.df

fit_submodel2 <- function(x,y=sub.dt2,meth='osa'){
  mak <- x[1]
  mod <- x[2]
  s_mod <- x[3]
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{b<-0}
  
  c <- a+b
  max.fit <- which.max(c)
    
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    score <- max(c)/2
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}


gettag <- function(x){
  k <- unlist(x)[1]
  k
}
getscore <- function(x){
  k <- unlist(x)[2]
  k  
}

tc<-tc %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel),1,fit_submodel2),
         fn_tag = sapply(fit_list,gettag),
         score = sapply(fit_list,getscore)) 

t3c <- tc %>% filter(fn_tag!=0)

t4c <- t3c %>% mutate(
  base_make = sub.dt2$make[fn_tag],
  base_model = sub.dt2$model[fn_tag],
  base_submodel = sub.dt2$submodel[fn_tag])

t4d <- t4c %>% select( finalmake,finalmodel,finalsubmodel,fn_tag,score,base_make,base_model,base_submodel)
```
```{r}
head(t4d,20)
```

```{r}
nrow <- dim(tc)[1]
sum(t4d[t4d$score==1,"score"])/nrow
sum(t4d[t4d$score>=0.9,"score"])/nrow
sum(t4d[t4d$score>=0.8,"score"])/nrow
sum(t4d[t4d$score>=0.5,"score"])/nrow
```



next add more variables

```{r}
colnames(big_dt) <- tolower(colnames(big_dt))

sub.dt2b <- big_dt %>% select(make, model, submodel,body_type,number_of_seats,transmission_type) %>% mutate_all(list(~tolower(.)))

head(sub.dt2b)
```

most will be 2, 5 or 7 

```{r seats}
sub.dt2b[sub.dt2b$number_of_seats==3,"number_of_seats"] <- 2
sub.dt2b[sub.dt2b$number_of_seats==4,"number_of_seats"] <- 5
sub.dt2b[sub.dt2b$number_of_seats==6,"number_of_seats"] <- 7
```
```{r}
sub.dt2c <- sub.dt2b %>% filter(number_of_seats==5 | number_of_seats==0 |number_of_seats==2| number_of_seats==7)
dim(sub.dt2c)
```

sedan = saloon
ute = utility
light/heavy van = van
sports car = coupe
self propelled caravan = rv/suv

```{r body_type}
sub.dt2c[sub.dt2c$body_type=="light van" | sub.dt2c$body_type=="heavy van","body_type"] <- "van"
sub.dt2c[sub.dt2c$body_type=="utility","body_type"] <- "ute"
sub.dt2c[sub.dt2c$body_type=="saloon","body_type"] <- "sedan"
sub.dt2c[sub.dt2c$body_type=="self propelled caravan","body_type"] <- "rv/suv"
sub.dt2c[sub.dt2c$body_type=="sports car","body_type"] <- "coupe"
```

cvt =  continuously variable 

```{r}
sub.dt2c[sub.dt2c$transmission_type=="continuously variable","transmission_type"] <- "cvt"
```
```{r}
sort(-table(sub.dt2c$number_of_seats))
```
```{R}
head(sub.dt2c)
```
```{r}
sub.dt2d <- unique(sub.dt2c)

dim(sub.dt2c)
dim(sub.dt2d)
```
```{r}

get.Seat <- function(x){
  x[x=="null"] <- NA
  x[x==0] <- NA
  noempty_x <- na.omit(x) # remove NA first
  noempty_table <- sort(-table(noempty_x)) # table of count in descending order
  new_table <- names(noempty_table) # attribute names from 'new_table'
  if(is.null(new_table)) {
     res = 0
     } else {
       res = new_table[1]
       # 1st should be the  majority
       if(length(new_table)>1 & noempty_table[1] == noempty_table[2]){
         res = x[1]} # get longest one if 1st = 2nd 
       
     }
   return(res) 
}
new.df2 <- new.df  %>% mutate(finalseats = apply(data.frame(seats,seats_n),1,get.Seat))
new.df2 <- new.df2 %>% select(finalmake,finalmodel,finalsubmodel,finalseats,transmission_n,body_style)
head(new.df2)
```

```{r}
save(new.df2,sub.dt2d,file="sim_data")
```
```{r}
load("sim_data")
```

```{R}
tc<-new.df2

fit_submodel2 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- unlist(x[1])
  mod <- unlist(x[2])
  s_mod <- unlist(x[3])
  seat <- unlist(x[4])
  trans <- unlist(x[5])
  body <- unlist(x[6])
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-stringsim("",y_sub[,"submodel"],method=meth)}
  
  c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  
  if(trans!="null"){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-stringsim("",y_sub[,"transmission_type"],method=meth)}
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- a+b+c+d+e
  
  max.fit <- which.max(tol)
    
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max(tol)/6
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}

gettag <- function(x){
  k <- unlist(x)[1]
  k
}
getscore <- function(x){
  k <- unlist(x)[2]
  k  
}
system.time(
te<-tc %>% select(finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style) %>%
  mutate(fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style),1,fit_submodel2),
         fn_tag = sapply(fit_list,gettag),
         score = sapply(fit_list,getscore)) 
)
t3e <- te %>% filter(fn_tag!=0)
```
```{r}
t3e <- t3e %>% mutate(
  base_make = sub.dt2d$make[fn_tag],
  base_model = sub.dt2d$model[fn_tag],
  base_submodel = sub.dt2d$submodel[fn_tag],
  base_seat = sub.dt2d$number_of_seats[fn_tag],
  base_transmission = sub.dt2d$transmission_type[fn_tag],
  base_body_style = sub.dt2d$body_type[fn_tag])

t4e <- t3e %>% select( finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style,fn_tag,score,base_make,base_model,base_submodel,base_seat,base_transmission,base_body_style)
head(t4e,20)
```

```{r}
nrow <- dim(te)[1]
dim(t4e[t4e$score==1,])[1]/nrow
dim(t4e[t4e$score>=0.9,])[1]/nrow
dim(t4e[t4e$score>=0.8,])[1]/nrow
dim(t4e[t4e$score>=0.5,])[1]/nrow
```


