---
title: "MOT_model_t"
author: "Kaiwen Lai"
date: "25/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(stringdist)
library(xlsx)
library(openxlsx)
```

```{r}
#df<-read.csv("../MOT Extract - Oct 2019.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
df<-read.xlsx("../MOT Exract Jul-Sep 2019.xlsx",1)

df_empty.ind <- apply(df, 1, function(x){
  sum(!is.na(x) & x !='' & !is.null(x))
}) 
df1 <- df[df_empty.ind!=0,]

sub.df <- df1 %>% select(make, make_n, mvrregmake_n, model, model_n, mvrregmodel_n, sub_model, submodel_n,mvrregsubmodel_n, body_style, seats, seats_n, transmission_n) %>% mutate_all(list(~tolower(.)))

get.Longest <- function(x){
  final.choice <- x[1]
  for(i in 1:length(x)){
    if(nchar(x[i])>nchar(final.choice)){
      final.choice <- x[i]
    }
  }
  final.choice
}

getModel <- function(x){
   x[x=="null"] <- NA
   x[x==""] <- NA
   noempty_x <- na.omit(x) # remove NA first
   noempty_table <- sort(-table(noempty_x)) # table of count in descending order
   new_table <- names(noempty_table) # attribute names from 'new_table'
   
   if(is.null(new_table)) {
     fn_code = 1
     res = "NONE" 
     } else {
       res = new_table[1]
       fn_code = 2
       # 1st should be the  majority
       if(length(new_table)>1 && noempty_table[1] == noempty_table[2]){
         res = get.Longest(new_table)
         fn_code = 3} # get longest one if 1st = 2nd 
       
     }
   return(res) 
}
```
```{r}
sub.df$seats<-ifelse(sub.df$seats!=0,sub.df$seats,sub.df$seats_n)

sub.df[sub.df$seats==3,"seats"] <- 2
sub.df[sub.df$seats==4,"seats"] <- 5
sub.df[sub.df$seats==6,"seats"] <- 7

new.df <- sub.df %>% mutate(
  finalmake = apply(data.frame(make, make_n, mvrregmake_n),1,getModel),
  finalmodel = apply(data.frame(model, model_n, mvrregmodel_n),1,getModel),
  finalsubmodel = apply(data.frame(sub_model, submodel_n,  mvrregsubmodel_n),1,getModel)) 
```

```{r}
head(new.df)
```

```{r}
stringsim("ca", c("abc","abd","cba","nba"),method="osa")
stringsim("ca", c("abc","abd","cba","nba"),method="lv")
stringsim("ca", c("abc","abd","cba","nba"),method="dl")
stringsim("ca", c("abc","abd","cba","nba"),method="hamming")
stringsim("ca", c("abc","abd","cba","nba"),method="lcs")
stringsim("ca", c("abc","abd","cba","nba"),method="qgram")
stringsim("ca", c("abc","abd","cba","nba"),method="cosine")
stringsim("ca", c("abc","abd","cba","nba"),method="jaccard")
stringsim("ca", c("abc","abd","cba","nba"),method="jw")
stringsim("ca", c("abc","abd","cba","nba"),method="soundex")
```






```{r}
dt1<-read.csv("../VehicleYear-2020.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt2<-read.csv("../VehicleYear-2019.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt3<-read.csv("../VehicleYear-2018.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt4<-read.csv("../VehicleYear-2017.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt5<-read.csv("../VehicleYear-2016.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt6<-read.csv("../VehicleYear-2015.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt7<-read.csv("../VehicleYear-2014.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt8<-read.csv("../VehicleYear-2013.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt9<-read.csv("../VehicleYear-2012.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)
dt10<-read.csv("../VehicleYear-2011.csv", header=TRUE, sep=',', stringsAsFactors=FALSE)

big_dt<-rbind(dt1,dt2,dt3,dt4,dt5,dt6,dt7,dt8,dt9,dt10)
```

```{r}
colnames(big_dt) <- tolower(colnames(big_dt))

sub.dt <- big_dt %>% select(make, model, submodel) %>% mutate_all(list(~tolower(.)))

dt_empty.ind <- apply(data.frame(sub.dt$submodel), 1, 
  function(x){
    sum(!is.na(x) & x !='' & !is.null(x))
}
)
sub.dt1 <- sub.dt[dt_empty.ind!=0,]

head(sub.dt1)
```


```{r}
sub.dt2 <- unique(sub.dt1)

dim(sub.dt1)
dim(sub.dt2)
```

```{r}
t1<-new.df
t2<-sub.dt2
#make,model,
```

```{r}
fit_submodel <- function(x,y=sub.dt2){
  sub_m <- x[2]
  mak <- x[1]
  
  if(sub_m!="NONE"){
    
    y_sub <- y[y[,1]==mak,]
    
    b<-stringsim(sub_m,y_sub[,"submodel"],method='osa')
    max.fit <- which.max(b)
    if(length(max.fit)==0){
      final.tag <- 0
    }else{
      a_sub <- y_sub[max.fit,"submodel"]
      a_make<- y_sub[max.fit,"make"]
      a_model <- y_sub[max.fit,"model"]
      final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    }
  }else{
    final.tag <- 0
  }
  
  final.tag
  
}


t1<-t1 %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_num = apply(data.frame(finalmake,finalsubmodel),1,fit_submodel))

head(t1,25)
```


How about the NONE sub-model?

```{r}
t3 <- t1 %>% filter(fit_num!=0)

t4 <- t3 %>% mutate( 
  base_make = sub.dt2$make[fit_num],
  base_model = sub.dt2$model[fit_num],
  base_submodel = sub.dt2$submodel[fit_num])
head(t4,20)
```
1. clean the source(make it smaller, get rid of duplicated value(same make,model,submodel))
2. filter the same make for each match, and get the highest similarity value as a result.



```{r}
dim(t4[t4$finalmodel==t4$base_model,])
```


Next, we try to find the record with same model and highest similarity of sub model.

```{R}
tb<-new.df

fit_submodel2 <- function(x,y=sub.dt2){
  mak <- x[1]
  mod <- x[2]
  s_mod <- x[3]
  
  if(s_mod!="NONE"){
    
    y_sub <- y[y[,1]==mak & y[,2]==mod,]
    
    b<-stringsim(s_mod,y_sub[,"submodel"],method='osa')
    max.fit <- which.max(b)
    if(length(max.fit)==0){
      final.tag <- 0
    }else{
      a_sub <- y_sub[max.fit,"submodel"]
      a_make<- y_sub[max.fit,"make"]
      a_model <- y_sub[max.fit,"model"]
      final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    }
  }else{
    final.tag <- 0
  }
  
  final.tag
  
}

tb<-tb %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_num = apply(data.frame(finalmake,finalmodel,finalsubmodel),1,fit_submodel2))

head(tb,25)

t3b <- tb %>% filter(fit_num!=0)

t4b <- t3b %>% mutate( 
  base_make = sub.dt2$make[fit_num],
  base_model = sub.dt2$model[fit_num],
  base_submodel = sub.dt2$submodel[fit_num])
head(t4b,20)
```
```{r}
dim(tb[tb$fit_num!=0,])
```

```{r}
head(tb[tb$fit_num==0,],20)
```


With the highest sum of similarity of model and submodel

```{R}
tc<-new.df

fit_submodel2 <- function(x,y=sub.dt2,meth='osa'){
  mak <- x[1]
  mod <- x[2]
  s_mod <- x[3]
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{b<-0}
  
  c <- a+b
  max.fit <- which.max(c)
    
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub)
    score <- max(c)/2
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}


gettag <- function(x){
  k <- unlist(x)[1]
  k
}
getscore <- function(x){
  k <- unlist(x)[2]
  k  
}

tc<-tc %>% select(finalmake,finalmodel,finalsubmodel) %>%
  mutate(fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel),1,fit_submodel2),
         fn_tag = sapply(fit_list,gettag),
         score = sapply(fit_list,getscore)) 

t3c <- tc %>% filter(fn_tag!=0)

t4c <- t3c %>% mutate(
  base_make = sub.dt2$make[fn_tag],
  base_model = sub.dt2$model[fn_tag],
  base_submodel = sub.dt2$submodel[fn_tag])

t4d <- t4c %>% select( finalmake,finalmodel,finalsubmodel,fn_tag,score,base_make,base_model,base_submodel)
```
```{r}
head(t4d,20)
```

```{r}
nrow <- dim(tc)[1]
sum(t4d[t4d$score==1,"score"])/nrow
sum(t4d[t4d$score>=0.9,"score"])/nrow
sum(t4d[t4d$score>=0.8,"score"])/nrow
sum(t4d[t4d$score>=0.5,"score"])/nrow
```



next add more variables

```{r}
colnames(big_dt) <- tolower(colnames(big_dt))

sub.dt2b <- big_dt %>% select(make, model, submodel,body_type,number_of_seats,transmission_type) %>% mutate_all(list(~tolower(.)))

head(sub.dt2b)
```

most will be 2, 5 or 7 

```{r seats}
sub.dt2b[sub.dt2b$number_of_seats==3,"number_of_seats"] <- 2
sub.dt2b[sub.dt2b$number_of_seats==4,"number_of_seats"] <- 5
sub.dt2b[sub.dt2b$number_of_seats==6,"number_of_seats"] <- 7
```
```{r}
sub.dt2c <- sub.dt2b %>% filter(number_of_seats==5 | number_of_seats==0 |number_of_seats==2| number_of_seats==7)
dim(sub.dt2c)
```

sedan = saloon
ute = utility
light/heavy van = van
sports car = coupe
self propelled caravan = rv/suv

```{r body_type}
sub.dt2c[sub.dt2c$body_type=="light van" | sub.dt2c$body_type=="heavy van","body_type"] <- "van"
sub.dt2c[sub.dt2c$body_type=="utility","body_type"] <- "ute"
sub.dt2c[sub.dt2c$body_type=="saloon","body_type"] <- "sedan"
sub.dt2c[sub.dt2c$body_type=="self propelled caravan","body_type"] <- "rv/suv"
sub.dt2c[sub.dt2c$body_type=="sports car","body_type"] <- "coupe"
```

cvt =  continuously variable 

```{r}
sub.dt2c[sub.dt2c$transmission_type=="continuously variable","transmission_type"] <- "cvt"
```
```{r}
sort(-table(sub.dt2c$number_of_seats))
```
```{R}
head(sub.dt2c)
```
```{r}
sub.dt2d <- unique(sub.dt2c)

dim(sub.dt2c)
dim(sub.dt2d)
```
```{r}

get.Seat <- function(x){
  x[x=="null"] <- NA
  x[x==0] <- NA
  noempty_x <- na.omit(x) # remove NA first
  noempty_table <- sort(-table(noempty_x)) # table of count in descending order
  new_table <- names(noempty_table) # attribute names from 'new_table'
  if(is.null(new_table)) {
     res = 0
     } else {
       res = new_table[1]
       # 1st should be the  majority
       if(length(new_table)>1 & noempty_table[1] == noempty_table[2]){
         res = x[1]} # get longest one if 1st = 2nd 
       
     }
   return(res) 
}
new.df2 <- new.df  %>% mutate(finalseats = apply(data.frame(seats,seats_n),1,get.Seat))
new.df2 <- new.df2 %>% select(finalmake,finalmodel,finalsubmodel,finalseats,transmission_n,body_style)
head(new.df2)
```

```{r}
save(new.df2,sub.dt2d,file="sim_data")
```
```{r}
load("sim_data")
```

```{R}
tc<-new.df2

fit_submodel2 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- unlist(x[1])
  mod <- unlist(x[2])
  s_mod <- unlist(x[3])
  seat <- unlist(x[4])
  trans <- unlist(x[5])
  body <- unlist(x[6])
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-0}
  
  c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  
  if(trans!="null"){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-0}
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- a+b+c+d+e
  
  max.fit <- which.max(tol)
  max.score <- tol[max.fit]
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max.score/5
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}

gettag <- function(x){
  k <- unlist(x)[1]
  k
}
getscore <- function(x){
  k <- unlist(x)[2]
  k  
}
```
```{r}
system.time(
te<-tc %>% select(finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style) %>%
  mutate(fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style),1,fit_submodel2),
         fn_tag = sapply(fit_list,gettag),
         score = sapply(fit_list,getscore)) 
)
t3e <- te %>% filter(fn_tag!=0)
```
```{r}
t3e <- t3e %>% mutate(
  base_make = sub.dt2d$make[fn_tag],
  base_model = sub.dt2d$model[fn_tag],
  base_submodel = sub.dt2d$submodel[fn_tag],
  base_seat = sub.dt2d$number_of_seats[fn_tag],
  base_transmission = sub.dt2d$transmission_type[fn_tag],
  base_body_style = sub.dt2d$body_type[fn_tag])

t4e <- t3e %>% select( finalmake,finalmodel,finalsubmodel, finalseats, transmission_n, body_style,fn_tag,score,base_make,base_model,base_submodel,base_seat,base_transmission,base_body_style)
head(t4e,20)
```

```{r}
nrow <- dim(te)[1]
dim(t4e[t4e$score==1,])[1]/nrow
dim(t4e[t4e$score>=0.9,])[1]/nrow
dim(t4e[t4e$score>=0.8,])[1]/nrow
dim(t4e[t4e$score>=0.5,])[1]/nrow
```

```{r}
t_data <- data.frame(tc$finalmake,tc$finalmodel,tc$finalsubmodel, tc$finalseats, tc$transmission_n, tc$body_style)

```
```{r}

fit_submodel4 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- as.character(unlist(x[1]))
  mod <- as.character(unlist(x[2]))
  s_mod <- as.character(unlist(x[3]))
  seat <- as.character(unlist(x[4]))
  trans <- as.character(unlist(x[5]))
  body <- as.character(unlist(x[6]))
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-ifelse(y_sub[,"submodel"]!="",0.5,0)
  }
  if(seat!="0"){
    c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  }else{
    c<-ifelse(y_sub[,"number_of_seats"]!="0",0.5,0)
  }
  
  if(trans!="null" | trans!=""){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-ifelse(y_sub[,"transmission_type"]!="",0.5,0)
  }
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- a+b+c+d+e
  
  max.fit <- which.max(tol)
  max.score <- tol[max.fit]
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max.score/5
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}
```

```{R}
te1<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="osa"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te1)[1]
dim(te1[te1$score==1,])[1]/nrow
dim(te1[te1$score>=0.9,])[1]/nrow
dim(te1[te1$score>=0.8,])[1]/nrow
dim(te1[te1$score>=0.5,])[1]/nrow


te2<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="lv"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te2)[1]
dim(te2[te2$score==1,])[1]/nrow
dim(te2[te2$score>=0.9,])[1]/nrow
dim(te2[te2$score>=0.8,])[1]/nrow
dim(te2[te2$score>=0.5,])[1]/nrow

te3<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="dl"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te3)[1]
dim(te3[te3$score==1,])[1]/nrow
dim(te3[te3$score>=0.9,])[1]/nrow
dim(te3[te3$score>=0.8,])[1]/nrow
dim(te3[te3$score>=0.5,])[1]/nrow

te4<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="hamming"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te4)[1]
dim(te4[te4$score==1,])[1]/nrow
dim(te4[te4$score>=0.9,])[1]/nrow
dim(te4[te4$score>=0.8,])[1]/nrow
dim(te4[te4$score>=0.5,])[1]/nrow

te5<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="lcs"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te5)[1]
dim(te5[te5$score==1,])[1]/nrow
dim(te5[te5$score>=0.9,])[1]/nrow
dim(te5[te5$score>=0.8,])[1]/nrow
dim(te5[te5$score>=0.5,])[1]/nrow

te6<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="qgram"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te6)[1]
dim(te6[te6$score==1,])[1]/nrow
dim(te6[te6$score>=0.9,])[1]/nrow
dim(te6[te6$score>=0.8,])[1]/nrow
dim(te6[te6$score>=0.5,])[1]/nrow

te7<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="cosine"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te7)[1]
dim(te7[te7$score==1,])[1]/nrow
dim(te7[te7$score>=0.9,])[1]/nrow
dim(te7[te7$score>=0.8,])[1]/nrow
dim(te7[te7$score>=0.5,])[1]/nrow

te8<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="jaccard"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te8)[1]
dim(te8[te8$score==1,])[1]/nrow
dim(te8[te8$score>=0.9,])[1]/nrow
dim(te8[te8$score>=0.8,])[1]/nrow
dim(te8[te8$score>=0.5,])[1]/nrow

te9<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="jw"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te9)[1]
dim(te9[te9$score==1,])[1]/nrow
dim(te9[te9$score>=0.9,])[1]/nrow
dim(te9[te9$score>=0.8,])[1]/nrow
dim(te9[te9$score>=0.5,])[1]/nrow

te10<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="soundex"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te10)[1]
dim(te10[te10$score==1,])[1]/nrow
dim(te10[te10$score>=0.9,])[1]/nrow
dim(te10[te10$score>=0.8,])[1]/nrow
dim(te10[te10$score>=0.5,])[1]/nrow
```

```{R}
tc<-new.df2

fit_submodel3 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- as.character(unlist(x[1]))
  mod <- as.character(unlist(x[2]))
  s_mod <- as.character(unlist(x[3]))
  seat <- as.character(unlist(x[4]))
  trans <- as.character(unlist(x[5]))
  body <- as.character(unlist(x[6]))
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-ifelse(y_sub[,"submodel"]!="",1,0)
  }
  
  c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  
  if(trans!="null"){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-ifelse(y_sub[,"transmission_type"]!="",1,0)
  }
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- a+b+c+d+e
  
  max.fit <- which.max(tol)
  max.score <- tol[max.fit]
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max.score/6
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}

te11<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel3,meth="osa"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te11)[1]
dim(te11[te11$score==1,])[1]/nrow
dim(te11[te11$score>=0.9,])[1]/nrow
dim(te11[te11$score>=0.8,])[1]/nrow
dim(te11[te11$score>=0.5,])[1]/nrow
```
```{r}
te11a <- te11 %>% filter(fn_tag!=0)

te11a <- te11a %>% mutate(
  base_make = sub.dt2d$make[fn_tag],
  base_model = sub.dt2d$model[fn_tag],
  base_submodel = sub.dt2d$submodel[fn_tag],
  base_seat = sub.dt2d$number_of_seats[fn_tag],
  base_transmission = sub.dt2d$transmission_type[fn_tag],
  base_body_style = sub.dt2d$body_type[fn_tag])

te11b <- te11a %>% select( tc.finalmake,tc.finalmodel,tc.finalsubmodel, tc.finalseats, tc.transmission_n, tc.body_style,fn_tag,score,base_make,base_model,base_submodel,base_seat,base_transmission,base_body_style)
```



```{R}

fit_submodel4 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- as.character(unlist(x[1]))
  mod <- as.character(unlist(x[2]))
  s_mod <- as.character(unlist(x[3]))
  seat <- as.character(unlist(x[4]))
  trans <- as.character(unlist(x[5]))
  body <- as.character(unlist(x[6]))
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-ifelse(y_sub[,"submodel"]!="",0.5,0)
  }
  if(seat!="0"){
    c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  }else{
    c<-ifelse(y_sub[,"number_of_seats"]!="0",0.5,0)
  }
  
  if(trans!="null" | trans!=""){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-ifelse(y_sub[,"transmission_type"]!="",0.5,0)
  }
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- a+b+c+d+e
  
  max.fit <- which.max(tol)
  max.score <- tol[max.fit]
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max.score/5
    }
  
  return(list("fn_tag" = final.tag,"score" = score)) 
}

te12<- t_data %>% 
  mutate(fit_list = apply(t_data,1,fit_submodel4,meth="osa"),
         score = sapply(fit_list,getscore),
         fn_tag = sapply(fit_list,gettag)) 

nrow <- dim(te12)[1]
dim(te12[te12$score==1,])[1]/nrow
dim(te12[te12$score>=0.9,])[1]/nrow
dim(te12[te12$score>=0.8,])[1]/nrow
dim(te12[te12$score>=0.5,])[1]/nrow
```

```{r}
te12a <- te12 %>% filter(fn_tag!=0)

te12a <- te12a %>% mutate(
  base_make = sub.dt2d$make[fn_tag],
  base_model = sub.dt2d$model[fn_tag],
  base_submodel = sub.dt2d$submodel[fn_tag],
  base_seat = sub.dt2d$number_of_seats[fn_tag],
  base_transmission = sub.dt2d$transmission_type[fn_tag],
  base_body_style = sub.dt2d$body_type[fn_tag])

te12b <- te12a %>% select( tc.finalmake,tc.finalmodel,tc.finalsubmodel, tc.finalseats, tc.transmission_n, tc.body_style,fn_tag,score,base_make,base_model,base_submodel,base_seat,base_transmission,base_body_style)
```

```{r}
te9a <- te10 %>% filter(fn_tag!=0)

te9a <- te9a %>% mutate(
  score_new = score*6/5,
  base_make = sub.dt2d$make[fn_tag],
  base_model = sub.dt2d$model[fn_tag],
  base_submodel = sub.dt2d$submodel[fn_tag],
  base_seat = sub.dt2d$number_of_seats[fn_tag],
  base_transmission = sub.dt2d$transmission_type[fn_tag],
  base_body_style = sub.dt2d$body_type[fn_tag])

nrow <- dim(te10)[1]
dim(te9a[te9a$score_new==1,])[1]/nrow
dim(te9a[te9a$score_new>=0.9,])[1]/nrow
dim(te9a[te9a$score_new>=0.8,])[1]/nrow
dim(te9a[te9a$score_new>=0.7,])[1]/nrow
dim(te9a[te9a$score_new>=0.6,])[1]/nrow
dim(te9a[te9a$score_new>=0.5,])[1]/nrow

te9b <- te9a %>% select( tc.finalmake,tc.finalmodel,tc.finalsubmodel, tc.finalseats, tc.transmission_n, tc.body_style,fn_tag,score_new,base_make,base_model,base_submodel,base_seat,base_transmission,base_body_style)
```

```{r}
save(te12,te2,te3,te4,te5,te6,te7,te8,te9,te10,file = "sim_rdata")
```


test another data set

```{r cars}
library(tidyverse)
library(dplyr)
library(xlsx)
library(openxlsx)
```


```
system.time(
te1<- tc %>% select(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style) %>%
  mutate(
    fit_list1 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="osa"),
    
    fit_list2 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="lv"),
    
    fit_list3 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="dl"),
    
    fit_list4 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="hamming"),
    
    fit_list5 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="lcs"),
    
    fit_list6 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="qgram"),
    
    fit_list7 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="cosine"),
    
    fit_list8 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="jaccard"),
    
    fit_list9 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="jw"),
    
    fit_list10 = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="soundex"),
    
    score1 = sapply(fit_list1,getscore),
    fn_tag1 = sapply(fit_list1,gettag),
    
    score2 = sapply(fit_list2,getscore),
    fn_tag2 = sapply(fit_list2,gettag),
    
    score3 = sapply(fit_list3,getscore),
    fn_tag3 = sapply(fit_list3,gettag),
    
    score4 = sapply(fit_list4,getscore),
    fn_tag4 = sapply(fit_list4,gettag),
    
    score5 = sapply(fit_list5,getscore),
    fn_tag5 = sapply(fit_list5,gettag),
    
    score6 = sapply(fit_list6,getscore),
    fn_tag6 = sapply(fit_list6,gettag),
    
    score7 = sapply(fit_list7,getscore),
    fn_tag7 = sapply(fit_list7,gettag),
    
    score8 = sapply(fit_list8,getscore),
    fn_tag8 = sapply(fit_list8,gettag),
    
    score9 = sapply(fit_list9,getscore),
    fn_tag9 = sapply(fit_list9,gettag),
    
    score10 = sapply(fit_list10,getscore),
    fn_tag10 = sapply(fit_list10,gettag)) 
)

get_sum_score<-function(x,dt=te1){
  nrow <- dim(dt)[1]
  print(dim(dt[dt[,x]==1,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.9,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.8,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.7,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.6,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.5,])[1]/nrow)
}

get_sum_score("score1")
get_sum_score("score2")
get_sum_score("score3")
get_sum_score("score4")
get_sum_score("score5")
get_sum_score("score6")
get_sum_score("score7")
get_sum_score("score8")
get_sum_score("score9")
get_sum_score("score10")
```

```{r}

system.time(
te2<- tc %>% select(r_id,finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style) %>%
  mutate(
    fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="cosine"),
    score = sapply(fit_list,gettag,num = 2),
    fn_tag = sapply(fit_list,gettag,num = 1),
    mod_score = sapply(fit_list,gettag,num=3),
    smod_score = sapply(fit_list,gettag,num=4)) 
)

get_sum_score<-function(x,dt=te2){
  nrow <- dim(dt)[1]
  print(dim(dt[dt[,x]==1,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.9,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.8,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.7,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.6,])[1]/nrow)
  print(dim(dt[dt[,x]>=0.5,])[1]/nrow)
}

get_sum_score("score")
```
```{R}
fit_submodel5 <- function(x,y=sub.dt2d,meth='osa'){
  mak <- as.character(unlist(x[1]))
  mod <- as.character(unlist(x[2]))
  s_mod <- as.character(unlist(x[3]))
  seat <- as.character(unlist(x[4]))
  trans <- as.character(unlist(x[5]))
  body <- as.character(unlist(x[6]))
  
  y_sub <- y[y[,1]==mak,]
  a<-stringsim(mod,y_sub[,"model"],method=meth)

  if(s_mod!="NONE"){
    b<-stringsim(s_mod,y_sub[,"submodel"],method=meth)
  }else{
    b<-0
  }
  if(seat!="0"){
    c <- stringsim(seat,y_sub[,"number_of_seats"],method=meth)
  }else{
    c<-0
  }
  
  if(trans!="null" | trans!=""){
    d<-stringsim(trans,y_sub[,"transmission_type"],method=meth)
  }else{
    d<-0
  }
  
  e <- stringsim(body,y_sub[,"body_type"],method=meth)
  
  tol<- 0.4*a+0.3*b+0.1*c+0.1*d+0.1*e
  
  max.fit <- which.max(tol)
  max.score <- tol[max.fit]
  mod.score <- a[max.fit]
  smod.score <- b[max.fit]
  seats.score <- c[max.fit]
  trans.score <- d[max.fit]
  body.score <- e[max.fit]
  
  if(length(max.fit)==0){
    final.tag <- 0
    score <- 0
  }else{
    a_sub <- y_sub[max.fit,"submodel"]
    a_make<- y_sub[max.fit,"make"]
    a_model <- y_sub[max.fit,"model"]
    a_seat <- y_sub[max.fit,"number_of_seats"]
    a_trans <- y_sub[max.fit,"transmission_type"]
    a_body <- y_sub[max.fit,"body_type"]
    final.tag <- which.max(y[,1]==a_make & y[,2]==a_model & y[,3]==a_sub & y[,5]==a_seat & y[,6]== a_trans & y[,4]==a_body)
    score <- max.score
    }
  
  return(list("fn_tag" = final.tag,"score" = score,"mod_score" = mod.score, "smod_score" = smod.score, "seats_score" = seats.score, "trans_score" = trans.score, "body_score" = body.score)) 
}
```

```{r}

te3<- tc %>% select(r_id,finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style) %>%
  mutate(
    fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel4,meth="jw"),
    score = sapply(fit_list,gettag,num = 2),
    fn_tag = sapply(fit_list,gettag,num = 1),
    mod_score = sapply(fit_list,gettag,num=3),
    smod_score = sapply(fit_list,gettag,num=4)) 

get_sum_score("mod_score",dt=te3)


te4<- tc %>% select(r_id,finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style) %>%
  mutate(
    fit_list = apply(data.frame(finalmake,finalmodel,finalsubmodel, finalseats, transmission, body_style),1,fit_submodel5,meth="jw"),
    score = sapply(fit_list,gettag,num = 2),
    fn_tag = sapply(fit_list,gettag,num = 1),
    mod_score = sapply(fit_list,gettag,num=3),
    smod_score = sapply(fit_list,gettag,num=4)) 

get_sum_score("mod_score",dt=te4)



```



